---
title: "Multiple linear regression"
author: "Amira Ibrahim"
date: "October 24, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
#Attach data
```{r DATASET_MULTIPLELINEARREGRESSION, echo=TRUE}
library(readr)
Multiple_Linear_regression <- read.csv(file.choose(),header = TRUE)
attach(Multiple_Linear_regression)
```
```{r, echo=TRUE}
names(Multiple_Linear_regression)
```
#check normality :
```{r, echo=TRUE}
library(moments)
skewness(HDL_LEVEL)
```
accepted range from -1 to +1
```{r, echo=TRUE}
kurtosis(HDL_LEVEL)
```
accepted range from -2 to +2 may to +3
```{r, echo=TRUE}
boxplot(HDL_LEVEL~Treatment , main="Relation between type of treatment & HDL level")
```
visually, data is normally distributed
```{r, echo=TRUE}
shapiro.test(HDL_LEVEL)
```
p-value > 0.05 , Fail to reject H0 , data is normally distributed

#test : H0 :mean of HDL level in new drug = mean of HDL level in placebo
```{r, echo=TRUE}
t.test(HDL_LEVEL~Treatment , mu =0 , paired= F , alternative="two.sided" ,conf.int=TRUE, conf.level=0.95)
```
p-value > 0.05 , Fail to reject H0 , No significant diffrence in mean between two types of treatment.

#Check correlation :
```{r,echo=TRUE}
cor(dummy_treatment, HDL_LEVEL)
# +ve very weak correlation
cor((dummy_treatment+dummy_sex), HDL_LEVEL)
# +ve weak correlation
```

##building regressin model 
```{r,echo=TRUE}
mlm1 <- lm(HDL_LEVEL~dummy_treatment , data = Multiple_Linear_regression)
summary(mlm1)
```
#test if sex is a cofounder
```{r,echo=TRUE}
mlm2 <- lm(HDL_LEVEL~dummy_treatment+dummy_sex , data = Multiple_Linear_regression)
summary(mlm2)
(0.5776 - 0.4696)*100
```
#there is 10.8 % change in coeffecient , Sex is confounder
```{r,echo=TRUE}
mlm3 <- lm(HDL_LEVEL~dummy_treatment+dummy_sex+(dummy_treatment*dummy_sex) ,
           data=Multiple_Linear_regression)
summary(mlm3)
```
#Y^ = b0+b1x1+b2x2+b3X1X2
HDL level in Male (NEW Drug) = 38.3079 + (1.0673*1) + (7.8753*1) + (-5.5033*1*1)

HDL level in Female (New Drug) = 38.3079 + (1.0673*1) + (7.8753*0) + (-5.5033*1*0)

#visualize the assumption
```{r,echo=TRUE}
plot(mlm3)
```

```{r, include=FALSE}
library(tinytex)
options(tinytex.verbose = TRUE)
```